---
title: "Getting Started with binominal"
author: "Aadiraj Batlaw"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to binominal}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(binominal)
```

## Binominal

The package `"binominal"` is a minimal implementation for simulating the binominal distribution for a given number of trials and a specified probability of each success, and to visualize the relative frequencies in such successes.


## Creating a `binominal random variable`

The first step is to create a `"binominal random variable"` object with the function `bin_distribution(trials, prob)`:

```{r}
myvar <- bin_variable(5, 0.3)
myvar
```
Use print.binvar() to view the binominal distribution in a more visually appealing format.
```{r}
print.binvar(myvar)
```

## Summary of binominal random variable

Once you have defined a `"binominal random variable"` object, you can use the function `summary()` to
output a summary of the random variable.

```{r}
sumVar <- summary(myvar)
sumVar
```

Use the print.summary.binvar() function to read it in a more visually appealing format.
```{r}
print.summary.binvar(myvar)
```


## Plot of success

You can use the bin_distribution function to get the distribution of the random variable.

```{r}
dis <- bin_distribution(5, 0.3)
dis
```
And then you can use the plot() function to visualize this distribution.

```{r, fig.show='hold'}
plot(dis)
```

You can use the bin_cumulative function to get the cumulative distribution of the random variable.

```{r}
cumul <- bin_cumulative(5, 0.3)
cumul
```
And then you can use the plot.bincums() function to visualizae this distribution.

```{r}
plot.bincums(cumul)
```


